Compositional equivalences based on Open pNets

### 2021-09-30 2016-Weak-FH-Bisim/WeakBisim.tex
ajoute un paragraphe sur les formats de regles dans "related work"

>>>>

There is also a clear relation with the seminal works on rule formats for Structured Operational Semantics, e.g. DeSimone format, GSOS, and conditional rules with or without negative premisses \cite{deSimone85,Bloom88bisimulationcant,GROOTE1992202,VANGLABBEEK2004229}.  Open pNets provides a way to define operators similar to these rules formats, but with quite different aim and approach. A formal comparison would be interesting, though not trivial. What we can say easily is that: the pNet format syntactically encompasses both DeSimone, GSOS, and conditional premisses rules. Then our compositionality result is more powerful than the classical result, but this is not a surprise, as it relies on a (sufficient) syntactic hypothesis on particular systems, rather than the general rules defining an operator.  Last, we intentionaly do not accept negative premisses, that would be more diffcult to put into practice in our implementation.
